noTCP: extend, extend, repurpose

### 2014-06-05 paper/paper.tex
added refs, a tiny restructuring, done for the day

@@

In this section we overview these different options, discuss their pros and cons and show how real networks interact with them. To that end, we have developed a simplified implementation of TCP that exchanges packets in the standard order (three-way handshake, data exchange and connection shutdown) but with various header fields modified to our purposes and without congestion or flow control since we only exchange two data packets once connection has been established (as well as any additional ones generated by middleboxes). We also do not consider packet resegmentation since the goal is to negotiate any endpoint-specific in packet headers so that correct behavior does not depend on how packets are split or coalesced together.

@@

Nevertheless, there are proposals that make use of them. One of the proposals for reducing Web latency~\cite{Flach:2013uy} suggests sending multiple copies of packets, but to avoid triggering duplicate acknowledgments add a reserved bit to the header. We confirmed the authors observation that middleboxes do not seem to discard packets with non-compliant TCP flags, however we also saw a number of middleboxes to clear such flags, hence interfering with the duplicate acknowledgmentof the proposed scheme.

@@

Window size field is potentially a better candidate, especially if used only during connection setup phase, since data is not typically transmitted during the handshake. We could further claim that even during data exchange a few of the least-significant bits could be sacrifised for carrying other information, however that would prevent flow control from operating properly. Higher-order bits could instead be given up when window scaling option is used to compensate for the derease of signalled window size, but for every such bit the maximum window would be halved, having negative effects for more capable clients connected though high capacity links. Finally, we observed many middleboxes to modify the field and there is a risk of the middleboxes using the initially negotiated one for assigning resources for the duration of the connection~\cite{}.

@@

Typically~\cite{} checksum recomputation is very simple: subtract the old header fields from the checksum and add the new ones to minimise the resouce use. In our sample X networks only do that, as indicated by the fact that they allow packets with incorrect checksums through towards the endpoint (otherwise the packet would either be dropped or a valid checksum would be recomputed). It is not always the case and another alternative is to add payload to a packet to make checksum a specific value. It can only be done when the receiving end is already expecting it, since it should not pass such payload up to the layer above, therefore can only be used from SYNACK onwards. A bigger issue here is that middleboxes do not always respect the standard and simply drop such packets even though the standard clearly allows handshake packets to contain payload~\cite{}:

@@

What is common to all candidate procol changes described above is that they are very limited in size and therefore can only be used to exchange an opcode rather and not a substantial amount of information. Such information must instead be exchanged through other means - either implicit to the opcode, or explicit by redefining the meaning of part of the data payload or previously exchanged information. We threfore focus on combining the above observations into a robust exchange of the opcode between two endpoints in current networks.

@@

Interestingly, on certain networks with what appears to be proxies deployed the behaviour is dependent on destination port used. In particular, they appear to be configured to allow traffic to commonly used SSL ports (443, 993) pass through unmodified. In fact, most of our attempted modifications are allowed through with the exception of packets that do not have a valid checksum being dropped.

@@

The main points of discussion on \emph{noTCP} is the same as with all TCP extensions: is it necessary, is it deployable and is it forwards-compatible? Furthermore, any special protocol negotiation still needs to be standardised to ensure compatibility at the Internet scale...

@@

In the context of MPTCP one proposal to add a generic control stream is to map such stream into a separate sequence number space and exchange control data over established subflows, only modifying MPTCP DSS option to use one of the reserved bits to differentiate the control stream from the data stream. Arguably the specified options are complex as well as extensible to enable it are precisely because there are very few ways in which TCP itself can be extended. the underlying assumption, however, is taht MPTCP is already deployed as well as that existing deployments will be forwards-compatible with the specification.

>>>>

\section{Methodology}

To test what works on current networks we have developed a simplified implementation of TCP that exchanges packets in the standard order (three-way handshake, data exchange and connection shutdown) but with various header fields modified to our purposes and without congestion or flow control since we only exchange two data packets once connection has been established (as well as any additional ones generated by middleboxes). We also currently do not consider packet resegmentation since the goal is to negotiate any endpoint-specific in packet headers so that correct behavior does not depend on how packets are split or coalesced together.

@@

In this section we overview these different options, discuss their pros and cons and show how real networks interact with them.

@@

Nevertheless, there are proposals that make use of them. One of the proposals for reducing Web latency~\cite{Flach:2013uy} suggests sending multiple copies of packets, but to avoid triggering duplicate acknowledgments add a reserved bit to the header. We confirmed the authors observation that middleboxes do not seem to discard packets with non-compliant TCP flags, however we also saw a number of middleboxes to clear such flags, hence interfering with the duplicate acknowledgment of the proposed scheme.

@@

Window size field is potentially a better candidate, especially if used only during connection setup phase, since data is not typically transmitted during the handshake. We could further claim that even during data exchange a few of the least-significant bits could be sacrificed for carrying other information, however that would prevent flow control from operating properly. Higher-order bits could instead be given up when window scaling option is used to compensate for the decrease of signaled window size, but for every such bit the maximum window would be halved, having negative effects for more capable clients connected though high capacity links. Finally, we observed many middleboxes to modify the field and there is a risk of the middleboxes using the initially negotiated one for assigning resources for the duration of the connection~\cite{}.

@@

In traditional NATs~\cite{Egevang:tu} checksum recomputation is very simple: subtract the old header fields from the checksum and add the new ones to minimize the resource use. In our sample X networks only do that, as indicated by the fact that they allow packets with incorrect checksums through towards the endpoint (otherwise the packet would either be dropped or a valid checksum would be recomputed). It is not always the case and another alternative is to add payload to a packet to make checksum a specific value. It can only be done when the receiving end is already expecting it, since it should not pass such payload up to the layer above, therefore can only be used from SYNACK onwards. A bigger issue here is that middleboxes do not always respect the standard and simply drop such packets even though the standard clearly allows handshake packets to contain payload~\cite{Postel:3EDyoxP_,Chu:2011tn}:

@@

What is common to all candidate protocol changes described above is that they are very limited in size and therefore can only be used to exchange an opcode rather and not a substantial amount of information. Such information must instead be exchanged through other means - either implicit to the opcode, or explicit by redefining the meaning of part of the data payload or previously exchanged information. We therefore focus on combining the above observations into a robust exchange of the opcode between two endpoints in current networks.

@@

Interestingly, on certain networks with what appears to be proxies deployed the behavior is dependent on destination port used. In particular, they appear to be configured to allow traffic to commonly used SSL ports (443, 993) pass through unmodified. In fact, most of our attempted modifications are allowed through with the exception of packets that do not have a valid checksum being dropped.

@@

The main points of discussion on \emph{noTCP} is the same as with all TCP extensions: is it necessary, is it deployable and is it forwards-compatible? Furthermore, any special protocol negotiation still needs to be standardized to ensure compatibility at the Internet scale...

@@

In the context of MPTCP one proposal to add a generic control stream is to map such stream into a separate sequence number space and exchange control data over established subflows, only modifying MPTCP DSS option to use one of the reserved bits to differentiate the control stream from the data stream. Arguably the specified options are complex as well as extensible to enable it are precisely because there are very few ways in which TCP itself can be extended. the underlying assumption, however, is that theyt MPTCP is already deployed as well as that existing deployments will be forwards-compatible with the specification.
